Manuscript Figures for Genome Biology

### 2018-08-29 manuscript_figures/manuscript_figures.Rmd
Adjust y-axis limits in Figure 6

# set alpha cutoff for plots that are fixed at a certain value of alpha
alpha <- 0.10
```

@@

```{r, Figure 6}
# RNAseq 
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[grepl("RNAseq", objects) & grepl("brain", objects) & !grepl("uninf", objects)] 
sb <- readRDS(file=resfile)
res <- data.frame(rowData(sb)) %>%
  dplyr::mutate(pval = assays(sb)$bench[,"unadjusted"])
pa <- strat_hist(res, pvalue = "pval",
           covariate = "ind_covariate", maxy = 10, axislabs = FALSE) +
  draw_plot_label("  RNA-seq case study: Brain", 0.5, 1, hjust = 0.5,fontface = "bold", 
                  size = 12) +
  draw_plot_label("Overall mean expression pvalue", size = 11, 0.5, 0.14, fontface = "plain",
                  hjust =0.5) +
  draw_plot_label("Density", size = 11, 0, 0.36, fontface = "plain", angle=90)

@@

pc <- strat_hist(res, pvalue = "pval",
           covariate = "ind_covariate", maxy = 7, axislabs = FALSE) +
  draw_plot_label("  GSEA case study: Mouse", 0.5, 1, hjust = 0.5, fontface = "bold" , size = 12) +
  draw_plot_label("Gene Set size pvalue", size = 11, 0.5, 0.14, fontface = "plain",
                  hjust =0.5) +
  draw_plot_label("Density", size = 11, 0, 0.36, fontface = "plain", angle=90)

>>>>

# set alpha cutoff for plots that are fixed at a certain value of alpha
alpha <- 0.05
```

@@

```{r, Figure 6}
# RNAseq 
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[grepl("RNAseq", objects) & grepl("brain", objects) & !grepl("uninf", objects)] 
sb <- readRDS(file=resfile)
res <- data.frame(rowData(sb)) %>%
  dplyr::mutate(pval = assays(sb)$bench[,"unadjusted"])
pa <- strat_hist(res, pvalue = "pval",
           covariate = "ind_covariate", maxy = 8.75, axislabs = FALSE) +
  draw_plot_label("  RNA-seq case study: Brain", 0.5, 1, hjust = 0.5,fontface = "bold", 
                  size = 12) +
  draw_plot_label("Overall mean expression pvalue", size = 11, 0.5, 0.14, fontface = "plain",
                  hjust =0.5) +
  draw_plot_label("Density", size = 11, 0, 0.36, fontface = "plain", angle=90)

@@

pc <- strat_hist(res, pvalue = "pval",
           covariate = "ind_covariate", maxy = 8.5, axislabs = FALSE) +
  draw_plot_label("  GSEA case study: Mouse", 0.5, 1, hjust = 0.5, fontface = "bold" , size = 12) +
  draw_plot_label("Gene Set size pvalue", size = 11, 0.5, 0.14, fontface = "plain",
                  hjust =0.5) +
  draw_plot_label("Density", size = 11, 0, 0.36, fontface = "plain", angle=90)
